Blocking-resistant communication through high-value web services

### 2014-05-13 docs/meek.tex
Acknowledgements.

tor-dev
tor-qa
George Kadianakis
Georg Koppen
Lunar
Yawning Angel
Vern Paxson
Nick Weaver

>>>>

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
